### 2018-09-11 doc/paper.tex
Removing "Future Work" heading from conclusion.
Replacing "Advancing Front" with "Expanding Front"
Per and I had discussed using BFS, but it isn't appropriate
because the algorithm isn't doing a search, it's covering
**all** elements / element pairs.

In order to compute \(M_{TD} \bm{d}\), we'll need to compute the
\emph{common refinement}, i.e. an intermediate mesh that contains
both the donor and target meshes. This will consist of all non-empty
\(\mathcal{T} \cap \mathcal{T}'\) as \(\mathcal{T}\) varies over
elements of the target mesh and \(\mathcal{T}'\) over elements of the
donor mesh. This requires solving three specific subproblems:
\begin{itemize}
%% H/T: https://tex.stackexchange.com/a/6086/32270
\itemsep 0em
\item Forming the region(s) of intersection between two elements that
  are B\'{e}zier triangles.
\item Finding all pairs of elements, one each from the target and donor mesh,
  that intersect.
\item Numerically integrating over a region of intersection between two
  elements.
\end{itemize}
The first subproblem is discussed in
Section~\ref{subsec:intersect-bez-tri}
and the curved polygon region(s) of intersection have been described
in Section~\ref{subsec:curved-polygons}. The second will be considered
in Section~\ref{subsec:advancing-front} and the third in
Section~\ref{subsec:integration-on-curved} below.

\subsection{Advancing Front}\label{subsec:advancing-front}

@@

Once we have such a match, we use the connectivity graph of the
donor mesh to perform a breadth first search
for neighbors that also intersect the target
element \(\mathcal{T}\) (Figure~\ref{fig:target-elt-overlap-extra-layer}).
This search takes \(\bigO{1}\) time. It's also worthwhile to keep the first
layer of donor elements that don't intersect \(\mathcal{T}\) because they are
more likely to intersect the neighbors of \(\mathcal{T}\)\footnote{In the
very unlikely case that the boundary of \(\mathcal{T}\)
\emph{exactly matches} the boundaries of the donor elements that cover it,
\emph{none} of the overlapping donor elements can intersect the neighbors of
\(\mathcal{T}\) so the first layer of non-intersected donor
elements must be considered.}. Using the list of intersected elements, a
neighbor of \(\mathcal{T}\) can find a donor element it intersects with in
\(\bigO{1}\) time (Figure~\ref{fig:target-elt-neighbor}).
As seen, after our \(\bigO{\left|\mathcal{M}_D\right|}\)
initial brute-force search, the localized intersections for each
target element \(\mathcal{T}\) take
\(\bigO{1}\) time. So together, the process takes
\(\bigO{\left|\mathcal{M}_D\right| + \left|\mathcal{M}_T\right|}\).

@@

The algorithm breaks down into three core subproblems: B\'{e}zier triangle
intersection, an advancing front for intersecting elements and
integration on curved polygons. The inherently local nature of the
advancing front allows the algorithm to be parallelized via domain
decomposition with little data shared between processes. By
restricting integration to the intersection of elements from the
target and donor meshes, the algorithm can accurately transfer
both continuous and discontinuous fields.

\subsection{Future Work}

>>>>

In order to compute \(M_{TD} \bm{d}\), we'll need to compute the
\emph{common refinement}, i.e. an intermediate mesh that contains
both the donor and target meshes. This will consist of all non-empty
\(\mathcal{T} \cap \mathcal{T}'\) as \(\mathcal{T}\) varies over
elements of the target mesh and \(\mathcal{T}'\) over elements of the
donor mesh. This requires solving three specific subproblems:
\begin{itemize}
%% H/T: https://tex.stackexchange.com/a/6086/32270
\itemsep 0em
\item Forming the region(s) of intersection between two elements that
  are B\'{e}zier triangles.
\item Finding all pairs of elements, one each from the target and donor mesh,
  that intersect.
\item Numerically integrating over a region of intersection between two
  elements.
\end{itemize}
The first subproblem is discussed in
Section~\ref{subsec:intersect-bez-tri}
and the curved polygon region(s) of intersection have been described
in Section~\ref{subsec:curved-polygons}. The second will be considered
in Section~\ref{subsec:expanding-front} and the third in
Section~\ref{subsec:integration-on-curved} below.

\subsection{Expanding Front}\label{subsec:expanding-front}

@@

Once we have such a match, we use the connectivity graph of the
donor mesh to perform a breadth-first search
for neighbors that also intersect the target
element \(\mathcal{T}\) (Figure~\ref{fig:target-elt-overlap-extra-layer}).
This search takes \(\bigO{1}\) time. It's also worthwhile to keep the first
layer of donor elements that don't intersect \(\mathcal{T}\) because they are
more likely to intersect the neighbors of \(\mathcal{T}\)\footnote{In the
very unlikely case that the boundary of \(\mathcal{T}\)
\emph{exactly matches} the boundaries of the donor elements that cover it,
\emph{none} of the overlapping donor elements can intersect the neighbors of
\(\mathcal{T}\) so the first layer of non-intersected donor
elements must be considered.}. Using the list of intersected elements, a
neighbor of \(\mathcal{T}\) can find a donor element it intersects with in
\(\bigO{1}\) time (Figure~\ref{fig:target-elt-neighbor}).
As seen, after our \(\bigO{\left|\mathcal{M}_D\right|}\)
initial brute-force search, the localized intersections for each
target element \(\mathcal{T}\) take
\(\bigO{1}\) time. So together, the process takes
\(\bigO{\left|\mathcal{M}_D\right| + \left|\mathcal{M}_T\right|}\).

@@

The algorithm breaks down into three core subproblems: B\'{e}zier triangle
intersection, a expanding front for intersecting elements and
integration on curved polygons. The inherently local nature of the
expanding front allows the algorithm to be parallelized via domain
decomposition with little data shared between processes. By
restricting integration to the intersection of elements from the
target and donor meshes, the algorithm can accurately transfer
both continuous and discontinuous fields.
